---
title: "The role of cognitive and personality characteristics in timely microcredit repayment: Evidence from a survey conducted by Provident, Mexico"
trans-title: "El papel de las características cognitivas y de personalidad en el pago oportuno de microcréditos: Evidencia de una encuesta realizada por Provident, México."
author:
- affiliation: CIDE
  email: daniel.ventosa@cide.edu
  first: Daniel 
  last: Ventosa-Santaulària
- affiliation: CIDE
  email: 
  first: Sonia
  last: Di Giannatale
- affiliation: CEMLA
  email: 
  first: María José
  last: Roa
- affiliation: CIDE
  email: 
  first: Alexander Alberto
  last: Elbittar
- affiliation: IFT
  email: 
  first: Dario
  last: Trujano 
abstract: Sustainability of microfinance institutions depends, among other factors, on having appropriate repayment levels. This article's contribution to existing literature is the analysis of the role of a personality trait named "grit" in individual microcredit repayment decisions, alongside cognitive characteristics and time and risk preferences. This study is based on a survey of a sample of clients at \'Provident México\', a formal microfinance institution that provides personal loans in vulnerable communities in Puebla, Mexico. We find evidence that, generally, older individuals possessing higher levels of grit and a tendency toward short term present bias are more likely to show no delays in loan repayments. Cognitive characteristics are inversely related to paying microcredits on time. Refinancing incentives does not play a key role in timely microcredit repayment, a result that is contrary to related literature but consistent with our finding that individuals in this sample that do not have delays in repayments are characterized by showing a short term present bias.
resumen: La sostenibilidad de las instituciones microfinancieras depende, entre otros factores, de tener niveles apropiados de repago. Este trabajo contribuye a la literatura existente al analizar el papel de un rasgo de personalidad denominado \"diligencia" ("grit" en inglés) en las decisiones de repago de microcréditos individuales, junto con las habilidades cognitivas y las preferencias de tiempo y riesgo. Este estudio se basa en una encuesta aplicada a una muestra de clientes en \'Provident México\', una institución formal de microfinanzas que ofrece préstamos personales en comunidades vulnerables en Puebla, México. Los resultados obtenidos indican que, en general, las personas mayores que poseen niveles más altos de diligencia, y que tienden a tener un sesgo por el corto plazo, tienen más probabilidades de no mostrar retrasos en el repago de los préstamos. Las características cognitivas están inversamente relacionadas con el pago de las deudas a tiempo. Los incentivos de refinanciamiento no desempeñan un papel clave en el repago a tiempo del microcrédito, contrario a la literatura. Sin embargo, en nuestra muestra, los resultados concuerdan con el sesgo por el corto plazo de los individuos que no tienen retrasos en sus pagos.
keywords:
  eng: Microcredit repayment; Personality traits; Grit; Cognitive characteristics; Time and risk preferences
  spa: Reembolso de microcréditos; Rasgos de personalidad; Determinación; Características cognitivas; Preferencias temporales y de riesgo
JEL: D12; D14
thanks: The authors wish to thank Provident México for their support in the development of this project. The questionnaire, the data generated by our empirical methodology, and the codes to estimate the econometric results are available in the online appendices.
bibliography: bibliography.bib
csl: apa.csl
firstpage: "1"
lastpage: "24"
month: May
art-num: 1
vol: 39
no: 1
year: 2020
date:
  received: "16 January 2019"
  accepted: "22 April 2020"
output:
  bookdown::html_document2:
    template: html-template.html
    numbersections: TRUE
    self_contained: TRUE
    mathjax-url: "https://cdn.jsdelivr.net/npm/mathjax@3/es5/tex-mml-chtml.js"
  bookdown::pdf_document2:
    template: template.tex
    toc: FALSE
    numbersections: TRUE
    css: ensayos.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rmarkdown)
library(bookdown)
library(htmltools)
```

# Introduction {-}

This paper analyzes microcredit repayment decisions of a sample of
individuals to whom \'Provident México\' (hereafter Provident), a formal
microfinance institution (MFI) based in Puebla (Mexico), had granted a
simple door-to-door personal loan. Specifically, the objective of this
research is to examine the hypothesis that cognitive characteristics as
well as personality traits and preferences play a role in microcredit
repayment behavior. This hypothesis is based on recent personality and
cognition theories, and the relevance of its examination is to gain
understanding on the determinants of vulnerable individuals' microcredit
repayment behavior for the sake of the well-being of individuals *per
se* and of the sustainability of MFIs.

MFIs represent the only source of access to formal credit for many
individuals in vulnerable socioeconomic conditions around the world
(Armendáriz de Aghion and Murdoch, 2010). Despite its importance,
evidence of the impact of microfinance on poverty reduction in
developing countries has been inconclusive (Hermes and Lensink, 2011).
Only recently evaluations of microfinance programs using the
randomized-controlled-trials (RCT) approach have been undertaken. The
RCT methodology is widely used in development economics for its
identification advantage, and it has received important recognition with
the awarding of the Nobel Prize in Economics in 2019 to Abhijit
Banerjee, Esther Duflo, and Michael Kremer for using this approach with
the objective of alleviating poverty, including the design and
evaluation of several microfinance initiatives. Evidence has been
reported that there are interventions where it is observed that
microfinance enhances consumption smoothing and expenditure in durable
goods (Banerjee et al., 2015), and investment in income-generating
activities (Augsburg et al., 2015; Crépon et al., 2015). However, 
certain studies report cases in which microcredits do
not show to have significative impacts on poverty relief (Angelucci et
al, 2015; Attanasio et al., 2015).

On the other hand, lending to the poor is costly due to elevated
transaction and information costs, which contributes to the high
interest rates that MFIs charge their clients, and MFIs must ensure an
appropriate repayment rate to be sustainable (Bauer *et al.*, 2012;
Nawai and Shariff, 2012; Baklouti, 2013; Van den Berg *et al*., 2015).
However, problems such as excessive professionalization of MFIs and
distancing from the original joint-liability loan format; clients'
over-indebtedness and its stressful consequences; and repayment problems
(Attanasio, et al., 2015; Banerjee et al., 2015), have cast a negative
light on microfinance as a vehicle for poverty alleviation.

The microfinance sector in Mexico began operating in the decade of the
50's with the creation of Sociedad de Cooperativas de Ahorro y Crédito
(Savings and Credit Cooperatives Society), and since then this sector
has experienced significant growth. Even though the interest rates that
Mexican MFIs charge their clients have shown a decreasing trend in
recent years, they are still higher than those charged by MFIs in other
Latin American countries. The reason seems to lie in the small average
size of microcredits which implies that MFIs in Mexico face high
operation costs and lack of efficiency in resource management (Cotler,
2013; Aldasoro, 2017). As pointed out by Griffin and Husted (2015), the
sustainability of an MFI depends on its repayment rate, and, given that
most of MFIs operating in Mexico offer group-base-lending, factors such
as social sanctions are of relevance when explaining repayment. However,
as mentioned above, Provident offers personal loans and as of 2014,
around 70% of its clients have shown delays in their payments. So, it is
reasonable to think that repayment of this type of microcredit is more
dependent on personal characteristics than with social issues. The novel
aspect of this research is the expansion of the set of personal
characteristics, based on recent contributions to the economic
literature that will be reviewed in the next section, that might play an
important role in timely microcredit repayment.

A survey applied to a random sample of clients of Provident, and
information provided by Provident on the microcredit repayment status of
this sample of clients are the sources of the dataset analyzed in this
paper. The results obtained from the econometric exercise performed here
indicate that older individuals possessing higher levels of grit and
with a tendency toward short term present bias are more likely to not
have delays in microcredit repayments. Cognitive characteristics results
are inversely related to timely debt repayment. Unexpectedly,
refinancing incentives do not play a key role on timely microcredit
repayment is played, but this result is consistent with our finding that
individuals in this sample that do not have delays in repayment are
characterized by showing a short term bias. It is worth observing that
most of the studies related to this article, that will be reviewed in
the next section, analyze financial decision-making in developed
economies, whereas this study is focused on microfinance repayment
behavior in a developing economy. Hence, this article's main
contribution to the literature is the addition of personality and
cognitive measures to the study of the microcredit repayment behavior in
a developing economy.

The rest of this paper is organized as follows. The next section
presents a review of the relevant literature with the purpose of laying
out a conceptual framework to justify the empirical model to be
estimated. In the third section, the empirical methodology and the unit of
analysis are described. In the fourth section, descriptive statistics of
the sample are presented. The formalization of the empirical model and
the econometric results are presented in the fifth section. Finally, in
the last section, conclusions are outlined and discussed.

# Literature Review

This article is related to several strands of the economic literature.
First, it contributes to the microcredits' repayment literature, in
which a general but not undisputed agreement exists that
sociodemographic characteristics are important factors in explaining
repayment behavior. Education and income have been shown to be
positively correlated to good microfinance repayment behavior (Bhatt and
Tang, 2002; and Shariff, 2012). The evidence on gender has been mixed: some studies find no
significant relationship between gender and repayment (D'Espallier *et
al.,* 2011), while others find that women, in general, are a better
credit risk for MFIs (Armendáriz and Murdoch, 2010).

Second, this study analyzes the importance of refinancing incentives in
repayment drawn by studies in microfinance. A group of studies have
demonstrated that the structure of the microfinance contracts plays a
role in repayment behavior. Without explicit incentives \-- such as
group liability or the use of non‐refinancing threats \-- borrowers tend
to be at least late on their repayment schedule (Bauer *et al.* 2012;
Nawai and Shariff, 2012; Baklouti, 2013). After evaluating several
microfinance experiences around the world, Armendáriz De Aghion and
Murdoch (2000) emphasize several mechanisms that help guarantee timely
individual credit repayment behaviors and avert some of the lateness
endemic in the microloan market. Said mechanisms include the
implementation of non-financial services, direct monitoring, regular
payment programs, and threats of non-refinancing that serve as dynamic
incentives.

Third, this work relates to studies that have shown the importance of
including cognitive characteristics when explaining individual
behaviors. The effect that cognitive characteristics have on a variety
of economic and social outcomes has been well documented (Almlund *et
al.,* 2011; Borghans *et al.,* 2011). An expanding body of work has
found that higher levels of cognitive abilities positively affect
financial habits in different ways: lower probability of default, fewer
financial errors, and greater sophistication in the use of financial
products (Christelis *et al.,* 2010; McArdle *et al.,* 2011; Grinblatt
*et al.*, 2011; Agarwal and Mazumder, 2013; Cole and Shastry, 2014).
These works primarily suggest that cognitive abilities -- and, of these,
numerical abilities in particular \-- are strongly related to making
appropriate financial decisions. In addition, there has been evidence of
a positive relationship between cognitive abilities and financial
literacy, defined by Lusardi and Mitchell (2014) as "people's ability to
process economic information and make informed decisions about financial
planning, wealth accumulation, debt, and pensions."

Fourth, this article brings together elements of recent studies that
have analyzed the role of personality traits in socioeconomic behaviors.
Psychologists have sketched a relatively commonly accepted taxonomy of
personality traits known as the 'Big Five': Openness to Experience,
Conscientiousness, Extroversion, Agreeableness and Neuroticism. Borghans
*et al.* (2011), Almlund *et al.* (2011), and Heckman and Kautz (2012)
reviewed evidence which indicates that these personality traits are as
powerful as cognitive abilities in predicting socioeconomic behaviors,
and that they are more malleable than cognitive characteristics over the
life cycle.

A group of pioneering studies has studied the relationship between
personality traits and financial behaviors. Some of these suggest that
the presence of a certain sub-facet related to Conscientiousness --
named grit or diligence \-- can explain wealth accumulation (Ameriks *et
al.*, 2003); financial distress (McCarthy, 2011); indebtedness and
default frequency (Klinger *et al.,* 2013 a, b); good management of
finances (Kaufmann, 2012); investment biases (Jamshidinavid *et al.,*
2012); and savings (Kausel *et al.,* 2016; Roa et al., 2019). In
general, grit is considered a measure of both the propensity to plan and
perseverance. Concerning microfinance, Klinger *et al.* (2013 a, b)
shows that Conscientiousness and Intelligence have a predictive power
similar to that of the usual metrics for evaluating loan repayment, such
as credit bureau data, while Honesty relates to willingness to repay a
loan. In addition, these authors found that Extroversion is strongly
related to high profits, while Agreeableness (positive),
Conscientiousness (negative) and Integrity (negative) are weakly
related. Some of these results are surprisingly stable across a variety
of countries, cultures and types of business.

Five risk and time preferences have been recognized by economists to
play a central role in financial decisions. In the case of credit
behavior, Meier and Sprenger (2010) find that individuals who are
present-biased show a higher probability of having credit card debts.
Regarding microfinance repayment behavior, there is evidence that
non-refinancing threats along with regular payment schedules can help
minimize problems of lack of self-control and present-biased preferences
(Bauer *et al.*, 2012; Basu, 2016).

Given the concepts and theoretical frameworks that have been explained
in the previous paragraphs, the objective at this point is to propose an
empirical model to explain the relationship between the probability that
an individual repays a microcredit on time (dependent variable) and the
following explanatory variables: (i) refinancing incentives: the
expectation is that having more than one microcredit with the
institution will have a positive effect on the probability of
microcredit repayment; (ii) sociodemographic characteristics: it is
expected that being a woman, having higher income and educational level,
and being older will positively impact the microcredit repayment
probability; (iii) conscientiousness (grit), and time and risk
preferences: it is important to clarify that the assumption that has
been made here, as in several other related studies (Almlund *et al.*,
2011), is that personality characteristics and preferences are
complements in explaining several economic behaviors, so they are
included as independent explanatory variables. That said, it is expected
that being grittier, more patient, and more risk averse all have a
positive relationship with the repayment probability; and finally, (iv)
cognitive characteristics and financial literacy: higher measured levels
of cognitive ability and of financial literacy are expected to be
positively related to the microcredit repayment probability.

In the next section, the fundamentals of the empirical methodology
employed in this article, i.e., the construction of the measures of
grit, cognitive ability and preferences, and the unit of analysis, will
be explained.

# Methodology and Unit of Analysis

## Measuring grit, cognitive ability, and preferences

The survey included a total of 16 questions and was designed to gather
information on the following variables: grit, cognitive characteristics,
time and risk preferences, basic financial knowledge, and
sociodemographic characteristics.[^1] In line with the personality
traits literature, the working hypothesis is that *grit* must be one of
the components of the set of attributes that comprise an individual's
sense of discipline when making long-term financial decisions. A
*gritty* or diligent individual might consider financial resources to be
a means to an end (the basic definition of money) and may want to ensure
a constant stream of monetary resources.

The Short Grit Scale (*Grit*-S) (Duckworth and Quinn, 2009), save one
question, is used to obtain a measure of grit. The first seven questions
of the questionnaire are taken and divided into two groups: Passion for
Long-term Goals (questions 1, 3, 5, and 6), and Perseverance of Effort
(questions 2, 4, and 7). Then, the scores for each answer are added up
and the sum is divided the result by 7 to obtain the individual's grit
indicator. *Grit*-S is a continuous variable with a maximum value of 5
(extraordinary *Grit* level), and a minimum of 1 (absence of *Grit*).

The level of an individual's cognitive ability was measured based on one
question (question 9) that is considered standard for this purpose
(Frederick, 2005). Financial knowledge was tested with two questions
(questions 12 and 13) from the OECD's Financial Literacy questionnaire
(OECD INFE, 2011; Lusardi and Mitchell 2014). These questions relate to
the calculation of interest rates and to the concept of inflation. The
interest rate question is sometimes considered a measure of numerical
abilities because it explicitly requires a calculation (Van Rooij *et
al.,* 2011; Gerardi *et al.,* 2013). That view is adopted here, hence
the interest rate question is considered a measure of numerical
abilities. Questions 9, 12 and 13, as well as the level of education
(question 14), will be used to measure cognitive ability in the
econometric analysis.

Information about time and risk preferences was obtained through three
questions, one for risk aversion (question 8) and two for time
preferences (questions 9 and 10). Finally, three questions about the
sociodemographic characteristics of the clients were included in the
survey: i) question 14, last school year completed; (ii) question 15,
civil status; and (iii) question 16, number of dependents.

## Unit of Analysis

The unit of analysis is Provident, a formal microfinance institution
based in Puebla (a state close to Mexico City), that grants simple
door-to-door personal loans, and which also operates in other parts of
the country. To be eligible for a personal loan, Provident requires that
the prospective client provide an official ID and proof of address. New
clients can apply for personal loans ranging from 1,000 to 7,500 Mexican
pesos (approximately 75.8-568.6 USD).[^2] If the client has a positive
credit history, this limit rises to 15,000 pesos per loan. Clients make
payments on a weekly basis over a period of up to 31, 41 or 51 weeks.
There is also an additional one-time charge that is determined at the
beginning of the loan (to cover administrative services, shipping,
weekly fee, and value-added tax), which is spread out weekly over the
loan's duration. There are no additional charges for late payments.
Provident has reported that most of the loans are used to purchase
consumer goods or to cover emergencies.

Provident classified its clients into three groups: *Current, Low
Arrear, and High Arrear*. It first decides on an initial date on which
to base the client's credit history. Clients who have made all their
weekly payments on time since that date are classified as Current; those
who have made 1-3 late payments over the period are classified as Low
Arrear; and finally, those who have been late in paying on more than
four occasions are classified as High Arrear.

Given the socioeconomic characteristics of its clients, Provident
expects some degree of lateness in the weekly payments and this
expectation is included in the calculation of the service charge the
clients must pay for their loans. However, the clients do not pay
interest on late payments. Also, Provident provides some incentives to
clients who pay their weekly payments on time. For example, a client
could receive a refinancing offer. On the other hand, a client is
eligible for another loan if he or she meets the following criteria:

1.  Person's age must be in the range of [18,71].

2.  The previous loan´s unpaid balance must be at most 32%.

3.  If there is another active client in the household, the total unpaid
    debt must not exceed \$55,000 if the collection rate in the previous
    13 weeks is lower than 83%; and \$70,000 otherwise.

Provident offered to obtain 100 completed questionnaires from each group
(*Current*, *Low Arrear*, and *High Arrear*), from the total of 2,475
clients that Provident selected as prospective members of our sample.
From the initial sample, the total number of complete interviews was
299: 99 *Current*, 100 *Low Arrear*, and 100 *High Arrear*. These
interviews were conducted by phone from the Provident's Call Center
between January and April 2014.[^3] It must be noted that during this
period, Provident had a total of 924,858 clients of which 28.2% were in
the *Current* group, while 56% and 15.8% were in the *Low* and *High
Arrear* groups, respectively. These weights were considered in the
regressions.

Finally, Provident provided the following information on the 299 clients
who completed the interviews: (i) sociodemographic variables: age;
number of children; employment status; gender; verifiable and
non-verifiable income; and home, cell phone, and landline ownership; and
(ii) financial records: number of loans (history); active loans;
monetary amount of active loans; total amount yet to be paid; monetary
amount of late payments; and weekly payment.

# Descriptive Statistics

As a first approach to the possible link among credit repayment and the
variables of interest, some patterns are outlined here. A more detailed
description of these patterns can be found in the On-line Appendix 2.
Here are some highlights that can be drawn from analyzing those
descriptive statistics:

(i) the probability of belonging to the Current group is slightly higher
    for an individual who is older than 35 years old, has fewer
    dependents, is a woman, and has a higher level of non-verifiable
    income.

(ii) the number of active loans monotonically decreases when moving from
    the *Current* group (1.36), *Low Arrear* group (1.19), and *High
    Arrear* group (0.6), in that order.

(iii) *Current* individuals obtain a *Grit* scale that is 0.10 times
    higher, on average, than that of the two other groups and a standard
    deviation of 5, also 0.7-0.9 times higher.

(iv) there are no significant differences in terms of short- and
    medium-term preferences among the groups, except for a noticeable
    preference for the short-term by the *Current* individuals. All
    groups display impatience in their answers preferring to receive
    their payments sooner rather than later.

(v) there is a negligible difference in the risk aversion level of the
    three groups, with the exception that the *High Arrear* group
    presents a level of risk aversion that is 7% higher than that of the
    *Low Arrear* group.

(vi) the *High Arrear* group proves to be above average in correct
    answers to the question that requires a simple interest calculation,
    and this group also has the highest standard deviation in the
    answers of this group with respect to those of the other two groups.
    Also, the *High Arrear* group shows the highest frequency of
    incorrect answers to the question about inflation, though there
    seems to be no significant difference with respect to the other two
    groups.

(vii) all of the answers to the question included to measure cognitive
    ability were incorrect and diverse. So, deviations with respect to
    the correct answer were calculated, and it is noticeable that, on
    average, people in the *High Arrear* group are closest to the
    correct answer, while individuals in the *Current* group are
    farthest from the correct answer.

(viii)  the difference between the *High* and *Low Arrear* groups in
    terms of Level of Schooling is not significant and, surprisingly,
    the *Current* group shows the highest proportion of individuals that
    have an Elementary School education or less.

<!-- -->

# Econometric Analysis and Results

## Empirical Model

As in Heckman *et al*. (2006), the empirical model that is analyzed in
this paper is based on the Roy model (Roy, 1951). To be precise, three
microcredit repayment levels, following the classification devised by
Provident, are used: *Current*, *Low Arrear* and *High Arrear*. Let $c$
be an individual's chosen microcredit repayment level, and $I_{c}$ the
individual's net profit associated with each microcredit repayment
level. Hence, the empirical model is:

```{r, eval=knitr::is_html_output(), echo=FALSE}
knitr::asis_output('$$')
```
\begin{equation} \label{eq:ic}
I_{c} = \beta_{c}X_{c} + \alpha_{c}^{P}f^{P} + \alpha_{c}^{C}f^{C} + \alpha_{c}^{N}f^{N} + e_{c}
\end{equation}
```{r, eval=knitr::is_html_output(), echo=FALSE}
knitr::asis_output('\\ (1) $$')
```

```{r, eval=knitr::is_html_output(), echo=FALSE}
knitr::asis_output('$$')
```
\begin{equation} \label{eq:set}
c\in\left\{current,\ low\ arrear,\ high\ arrear\right\}:\ microcredit\ repayment\ level 
\end{equation}
```{r, eval=knitr::is_html_output(), echo=FALSE}
knitr::asis_output('\\ (2) $$')
```

where $X_{c}$ is a vector of observed sociodemographic characteristics
of the individual that affect microcredit repayment behavior,
$\beta_{c}$ is its vector of parameters, $f^{P}$ is the individual's
time and risk preference, $f^{C}$ is the individual's level of cognitive
ability,$\ f^{N}$ is the individual's Grit Scale; $\alpha_{c}^{P}$,
$\alpha_{c}^{C}$ and $\alpha_{c}^{N}$ are parameters associated with
time and risk preferences, cognitive ability and Grit Scale score,
respectively, and $e_{c}$ represents an idiosyncratic component assumed
to be independent from $X_{c}$, $f^{P}$, $f^{C}$ and $f^{N}$. It is
assumed that time and risk preferences, cognitive ability, and Grit
Scale are independent, as mentioned in the last paragraph of the
Literature Review.

An individual chooses his or her microcredit repayment level such that:

```{r, eval=knitr::is_html_output(), echo=FALSE}
knitr::asis_output('$$')
```
\begin{equation} \label{eq:dc}
D_{c} = \operatorname{argmax}\left\{ I_{c} \right\}_{c \in \left\{ current,low\ arrear,\ high\ arrear \right\}}
\end{equation}
```{r, eval=knitr::is_html_output(), echo=FALSE}
knitr::asis_output('\\ (3) $$')
```

where $D_{c}$ denotes the individual's choice. Equations (1) and (2)
produce a standard discrete choice model with a structure factor
(Heckman, 1981). Following Heckman *et al*. (2006), $f^{P}$, $f^{C}$ and
$f^{N}$ can be interpreted as approximations to the basic parameters of
preferences, cognitive ability, and personality traits. In doing so, it
is assumed that these concepts play a complementary role in explaining
the results for microcredit repayment behavior (Almlund *et a*l., 2011;
Becker *et al*., 2012; Rustichini *et al*., 2016). Possible directions
of causality are not taken into consideration here.

## Results

The model is estimated as a weighted[^4] ordered logistic model (ordered
logit, for short).[^5] The dependent variable was the classification of
the client in the group Current, Low or High, as a function of late
payments. The model is parametrized as:

```{r, eval=knitr::is_html_output(), echo=FALSE}
knitr::asis_output('\n\n $$ log (  P(G\\leq g)/ P(G>g) )  = \\beta_{g0} + \\beta X_{c} + \\alpha^{P} f^{P} + \\alpha^{C} f^{C} + \\alpha^{N} f^{N} $$ \n\n')
```

```{r, eval=knitr::is_latex_output(), echo=FALSE}
knitr::asis_output('\n\n\\begin{equation*}
log \\left(  \\frac{P(G\\leq g)}{P(G>g)} \\right)  = \\beta_{g0} + \\beta X_{c} + \\alpha^{P} f^{P} + \\alpha^{C} f^{C} + \\alpha^{N} f^{N}
\\end{equation*}\n\n')
```

where $P(G \leq g)$ is the probability of belonging to the group g or
lower (Current\<Low \<High). The model is based on the proportional odds
assumption, which allows for calculating the same coefficients for every
group. In this regression, the choosen variable $D_{c}$ is modeled as a
random variable with higher probability for late payments as a function
of a latent variable that can be interpreted as $I_{c}$. Note that in
this parametrization we are considering that the parameters are equal
across groups, except for the intercept. This implicitly assumes that
the effects are equal, and the final decision depends only on the level
of covariates. This setting allows to analyze the variables of interest
at the population level. The proportional odds assumption was evaluated
graphically, and the Brant test cannot reject this hypothesis. The
result of this analysis is presented in the online appendix.

The primary goal is to explain the effects of each factor or concept on
the response probability (belonging to a specific group, i.e., Current,
Low or High). Given that the latent variable does not have a
well-defined unit of measurement, the magnitudes of each estimated
parameter cannot be considered meaningful. As this is well known in the
literature, we estimate the partial effect of roughly continuous
variables on the response probability. These are referred to as marginal
effects.

The measurement of cognitive ability deserves a further comment. The
latter can be imperfectly proxied or measured through questions 9
(baseball quad), 12 and 13 (financial knowledge), and 14 (level of
education); the rather poor performance of the respondents to questions
9,12, and 13 leads us to suspect that, although informative, the
aforementioned questions are not perfect measures of cognitive ability.
Therefore, a cognitive ability index, CA1, is built to maximize the
information via a Principal Component Analysis (PCA), using the
eigenvalues (weights).[^6] This approach allows us to avoid having
collinearities whilst simultaneously using most of the available
information. Out of the four variables included to build the CA1 index,
scholarship (question 14) and interest rate or numerical ability
(question 13) bear the most important weight. The index holds almost 30%
of the total variance of these four variables.[^7] The mean of the
variables considered for the regression model can be seen in Table 1.


```{=latex}
\input{table1}
```

```{=html}
<div style="overflow-x:auto;">
  <table>
      <caption>Table1: Average conditional to group. *This section displays the quantity of people in each group and each education level.</caption>
      <tr>
      <th rowspan="2">   Group   </th>
      <th rowspan="2">   Grit   </th>
      <th rowspan="2">   Short Delay   </th>
      <th rowspan="2">   Long Delay   </th>
      <th rowspan="2">   CA1   </th>
      <th rowspan="2">   Age   </th>
      <th rowspan="2">   Active Loans   </th>
      <th rowspan="2">   Female   </th>
      <th rowspan="2">   Q9. Baseball quad   </th>
      <th rowspan="2">   Q12. Interest   </th>
      <th rowspan="2">   Q13. Inflation   </th>
      <th colspan="5">   Education*   </th>
    </tr>
    <tr>
      <th>   Primary     </th>
      <th>   Secondary   </th>
      <th>High school    </th>
      <th>College        </th>
      <th>Grade          </th>
    </tr>
    <tr>
      <td>&nbsp;&nbsp;&nbsp;Current&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;2.318&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;0.12&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;0.18&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;-0.0544&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;40.1&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;1.3&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;66%&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;56.2&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;5131&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;0.374&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;40&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;32&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;20&nbsp;&nbsp;&nbsp;</td>
      <td>6</td>
      <td>1</td>
    </tr>
    <tr>
      <td>&nbsp;&nbsp;&nbsp;Low Arrear&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;2.217&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;0.24&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;0.24&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;0.0183&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;40.9&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;1.2&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;64%&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;49.7&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;3706&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;0.36&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;33&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;38&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;26&nbsp;&nbsp;&nbsp;</td>
      <td>3</td>
      <td>0</td>
    </tr>
    <tr>
      <td>&nbsp;&nbsp;&nbsp;High arrear&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;2.213&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;0.27&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;0.17&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;0.0355&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;35.4&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;0.6&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;61%&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;41.8&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;4585&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;0.44&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;30&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;32&nbsp;&nbsp;&nbsp;</td>
      <td>&nbsp;&nbsp;&nbsp;29&nbsp;&nbsp;&nbsp;</td>
      <td>8</td>
      <td>0</td>
    </tr>
  </table>
</div>
<p></p>
```


The main results[^8] can be seen in regression (1) in Table 2. Note that
the five covariates are statistically significant at the one percent
level. These regressions consider the weights of the proportion of the
groups in the population; however, the conclusion is the same as those
of the regression that does not consider the weights as can be noticed
in regression (1) of Table 5. Adding the weights provide more accurate
estimates of the coefficients.


```{=latex}
\input{reg1.tex}
```

```{=html}
<div style="overflow-x:auto;">
  <table>
      <caption>Table 2: Regressions Considering Weights</caption>
      <tr>
        <th>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</th>
        <th colspan="2">&nbsp;&nbsp;&nbsp;Dependent Variable&nbsp;&nbsp;&nbsp;</th>
      </tr>
      <tr>
        <th>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;  </th>
        <th>&nbsp;&nbsp;&nbsp;(1)&nbsp;&nbsp;&nbsp;</th>
        <th>&nbsp;&nbsp;&nbsp;(2)&nbsp;&nbsp;&nbsp;</th>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;Grit&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.446***&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.528***&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;(0.044)&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;(0.046)&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;Short Delay&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;0.919***&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;0.781***&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;(0.059)&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;Long Delay&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.448***&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.364***&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;(0.057)&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;(0.019)&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;CA1&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;0.100***&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;0.146***&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;(0.019)&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;(0.019)&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;Age&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.018***&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.012***&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;(0.002)&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;(0.002)&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;Active loans&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-1.550***&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;(0.039)&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;AIC&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;18973.63&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;17317.37&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;BIC&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;19024.08&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;17375.03&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;Observations&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;9972&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;9972&nbsp;&nbsp;&nbsp;</td>
      </tr>
  </table>
</div>
<p></p>
```


Relevant inference (sign and magnitude) should nonetheless be drawn from
the marginal effects, which can be obtained for each arrear. The
marginal effects of regression (1) are shown in Table 3.



```{=latex}
\input{reg2}
```

```{=html}
<div style="overflow-x:auto;">
  <table>
    <caption>Table 3: Marginal Effects (1). Note: All marginal effects are significant at the 1% level.</caption>
      <tr>
        <th>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</th>
        <th>&nbsp;&nbsp;&nbsp;Current&nbsp;&nbsp;&nbsp;</th>
        <th>&nbsp;&nbsp;&nbsp;Low Arrear&nbsp;&nbsp;&nbsp;</th>
        <th>&nbsp;&nbsp;&nbsp;High arrear&nbsp;&nbsp;&nbsp;</th>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;Grit&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;0.087&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.028&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.059&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;Short Delay&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.156&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;0.012&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;0.144&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;Long Delay&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;0.093&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.039&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.054&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;CA1&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.019&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;0.006&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;0.013&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;Age&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;0.003&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.001&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.002&nbsp;&nbsp;&nbsp;</td>
      </tr>
    </table>
</div>
<p></p>
```



Notice that all the marginal effects are statistically different from
zero and have the expected sign in all but one case, cognitive ability.
From our econometric results, we can draw the following conclusions.

Firstly, the probability of belonging to the *Current* group:

(i) Increases 8.7% the grittier the individual is.

(ii) Decreases 15.6% the more present-biased in the short term (Short
    Delay) the individual is [Question 10]

(iii) Increases 9.3% the more present-biased in the medium term (Long
    Delay) the individual is, [Question 11]

(iv) Decreases 1.9% the higher cognitive ability (CA1) the individual
    shows, and

(v) Increases 0.3% the older the individual is.

Secondly, the probability of belonging to the *Low arrear* (*High
arrear*\--in parenthesis) group:

(vi) Decreases 2.8% (-5.9%) the grittier the individual is.

(vii) Increases 1.2% (14.4%) the more present-biased in the short term
    (Short Delay) the individual is [Question 10].

(viii)  Decreases 3.9% (5.4%) the more present-biased the individual in
    the medium term (Long Delay) is, [Question 11].

(ix) Increases 0.6% (1.3%) the higher cognitive ability (CA1) the
    individual shows, and

(x) Decreases 0.1% (0.2%) the older the individual is.

## Including refinancing incentives

As a second econometric exercise, a regression similar to the previous
one is run but including a variable that measures the number of active
credits the individuals have with this institution. The regression
estimates appear in Table 1, regression (2). Note again that the
numerical values and the sign remain unchanged. The marginal effects are
barely affected, see Table 4:



```{=latex}
\input{me2}
```

```{=html}
<div style="overflow-x:auto;">
        <table>
        <caption>Table 4: Marginal Effects (2)</caption>
      <tr>
        <th>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</th>
        <th>&nbsp;&nbsp;&nbsp;Current&nbsp;&nbsp;&nbsp;</th>
        <th>&nbsp;&nbsp;&nbsp;Low Arrear&nbsp;&nbsp;&nbsp;</th>
        <th>&nbsp;&nbsp;&nbsp;High arrear&nbsp;&nbsp;&nbsp;</th>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;Grit&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;0.088&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.021&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.067&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;Short Delay&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.113&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.002&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;0.0115&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;Long Delay&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;0.064&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.022&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.042&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;CA1&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.024&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;0.006&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;0.018&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;Age&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;0.002&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;&lt;0.001&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.002&nbsp;&nbsp;&nbsp;</td>
      </tr>
      <tr>
        <td>&nbsp;&nbsp;&nbsp;Active loans&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;0.257&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.062&nbsp;&nbsp;&nbsp;</td>
        <td>&nbsp;&nbsp;&nbsp;-0.196&nbsp;&nbsp;&nbsp;</td>
      </tr>
    </table>
</div>
<p></p>
```



Note that age becomes less important and being present-biased now
affects positively via question 10 the probability of belonging to the
*Low Arrear* group (again, the effect is rather small). The interesting
part is that, when the individual is participating in only one loan, her
probability of being in the *Current* group increases by 25.7%, whilst
it has a small effect in the probability of belonging to the *Low
Arrear* group (-6.2%) and the probability of belonging to the *High
Arrear* group diminishes by 19.6%.

Several robustness checks (4 control regressions to be precise, labeled
Control 1, 2, 3, 4) were performed, and the results are presented in
Table 5. Regressions (1) and (2) in Table 5 are identical to those in
Table 1 except that the population weights (of current, low and high
arrear) are not considered. The rest of the regressions consider
population weights. In regression (3) the variable Age is excluded, in
(4) CA1 is excluded, in (5) Long delay is excluded, in (6) Short Delay
is excluded, and in (7) Grit is excluded. The estimated parameters and
their sign remain unchanged in every robustness check.



```{=latex}
\input{reg3}
```

```{=html}
<div style="overflow-x:auto; margin:auto">
    <table>
      <caption> Table 5: Regressions Considering Weights. Note: *p < 0.1; **p < 0.05; ***p < 0.01. 1 The first two regressions are equal to regressions (1) and (2) in Table 1 but without considering weights. </caption>
  <tr>
    <th></th>
    <th colspan="8">&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;Dependent Variable&nbsp;&nbsp;&nbsp;&nbsp;</th>
  </tr>
  <tr>
    <th>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</th>
    <th colspan="2">   Without Weights<sup>1</sup>  <br></th>
    <th></th>
    <th colspan="5">&nbsp;&nbsp;&nbsp;Weighted&nbsp;&nbsp;&nbsp;</th>
  </tr>
  <tr>
    <th>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;  </th>
    <th>&nbsp;&nbsp;&nbsp;(1)&nbsp;&nbsp;&nbsp;</th>
    <th>&nbsp;&nbsp;&nbsp;(2)&nbsp;&nbsp;&nbsp;</th>
    <th></th>
    <th>&nbsp;&nbsp;&nbsp;(3)&nbsp;&nbsp;&nbsp;</th>
    <th>&nbsp;&nbsp;&nbsp;(4)&nbsp;&nbsp;&nbsp;</th>
    <th>&nbsp;&nbsp;&nbsp;(5)&nbsp;&nbsp;&nbsp;</th>
    <th>&nbsp;&nbsp;&nbsp;(6)&nbsp;&nbsp;&nbsp;</th>
    <th>&nbsp;&nbsp;&nbsp;(7)&nbsp;&nbsp;&nbsp;</th>
  </tr>
  <tr>
    <td>&nbsp;&nbsp;&nbsp;Grit&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-0.465*&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-0.476*&nbsp;&nbsp;&nbsp;</td>
    <td></td>
    <td>&nbsp;&nbsp;&nbsp;-0.498***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-0.503***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-0.538***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-0.519***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
  </tr>
  <tr>
    <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.240)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.259)&nbsp;&nbsp;&nbsp;</td>
    <td></td>
    <td>&nbsp;&nbsp;&nbsp;(0.045)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.045)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.046)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.045)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
  </tr>
  <tr>
    <td>&nbsp;&nbsp;&nbsp;Short Delay&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;1.009***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;0.723**&nbsp;&nbsp;&nbsp;</td>
    <td></td>
    <td>&nbsp;&nbsp;&nbsp;0.752***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;0.760***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;0.580***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;0.769***&nbsp;&nbsp;&nbsp;</td>
  </tr>
  <tr>
    <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.316)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.333)&nbsp;&nbsp;&nbsp;</td>
    <td></td>
    <td>&nbsp;&nbsp;&nbsp;(0.059)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.059)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.050)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.059)&nbsp;&nbsp;&nbsp;</td>
  </tr>
  <tr>
    <td>&nbsp;&nbsp;&nbsp;Long Delay&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-0.609*&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-0.343&nbsp;&nbsp;&nbsp;</td>
    <td></td>
    <td>&nbsp;&nbsp;&nbsp;-0.321***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-0.392***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;0.065&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-0.389***&nbsp;&nbsp;&nbsp;</td>
  </tr>
  <tr>
    <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.319)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.335)&nbsp;&nbsp;&nbsp;</td>
    <td></td>
    <td>&nbsp;&nbsp;&nbsp;(0.059)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.059)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.049)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.059)&nbsp;&nbsp;&nbsp;</td>
  </tr>
  <tr>
    <td>&nbsp;&nbsp;&nbsp;CA1&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;0.090&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;0.133&nbsp;&nbsp;&nbsp;</td>
    <td></td>
    <td>&nbsp;&nbsp;&nbsp;0.138***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;0.154***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;0.134***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;0.130***&nbsp;&nbsp;&nbsp;</td>
  </tr>
  <tr>
    <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.102)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.108)&nbsp;&nbsp;&nbsp;</td>
    <td></td>
    <td>&nbsp;&nbsp;&nbsp;(0.019)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.019)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.019)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.019)&nbsp;&nbsp;&nbsp;</td>
  </tr>
  <tr>
    <td>&nbsp;&nbsp;&nbsp;Age&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-0.027***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-0.017*&nbsp;&nbsp;&nbsp;</td>
    <td></td>
    <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-0.012***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-0.011***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-0.011***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-0.011***&nbsp;&nbsp;&nbsp;</td>
  </tr>
  <tr>
    <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.009)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.010)&nbsp;&nbsp;&nbsp;</td>
    <td></td>
    <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.002)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.002)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.002)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.002)&nbsp;&nbsp;&nbsp;</td>
  </tr>
  <tr>
    <td>&nbsp;&nbsp;&nbsp;Active loans&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-1.772***&nbsp;&nbsp;&nbsp;</td>
    <td></td>
    <td>&nbsp;&nbsp;&nbsp;-1.576***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-1.531***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-1.560***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-1.579***&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;-1.530***&nbsp;&nbsp;&nbsp;</td>
  </tr>
  <tr>
    <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp; &nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.223)&nbsp;&nbsp;&nbsp;</td>
    <td></td>
    <td>&nbsp;&nbsp;&nbsp;(0.039)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.039)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.039)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.039)&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;(0.039)&nbsp;&nbsp;&nbsp;</td>
  </tr>
  <tr>
    <td>&nbsp;&nbsp;&nbsp;AIC&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;648.59&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;574.49&nbsp;&nbsp;&nbsp;</td>
    <td></td>
    <td>&nbsp;&nbsp;&nbsp;17370.44&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;17373.04&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;17353.48&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;17490.24&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;17450.48&nbsp;&nbsp;&nbsp;</td>
  </tr>
  <tr>
    <td>&nbsp;&nbsp;&nbsp;BIC&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;674.49&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;604.09&nbsp;&nbsp;&nbsp;</td>
    <td></td>
    <td>&nbsp;&nbsp;&nbsp;17420.89&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;17423.49&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;17403.93&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;17540.69&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;17500.93&nbsp;&nbsp;&nbsp;</td>
  </tr>
  <tr>
    <td>&nbsp;&nbsp;&nbsp;Observations&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;299&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;299&nbsp;&nbsp;&nbsp;</td>
    <td></td>
    <td>&nbsp;&nbsp;&nbsp;9,972&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;9,972&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;9,972&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;9,972&nbsp;&nbsp;&nbsp;</td>
    <td>&nbsp;&nbsp;&nbsp;9,972&nbsp;&nbsp;&nbsp;</td>
  </tr>
</table>
</div>
<p></p>
```



# Discussion and Conclusions

The main findings of the paper are as follows. First, a *grittier*, more
present-biased, and older individual is less likely to delay their loan
repayments. That older individuals repay on time is expected. The grit
result is in line with related literature that highlights the key role
of conscientiousness and its sub-facets in desirable economic and
financial decision-making (Eskreis-Winkler *et al*., 2014). Despite
having only recently been integrated within the literature on financial
decision-making, personality traits seem to constitute a key element in
explaining financial behaviors, as they do in other social and economic
behaviors. For future research, we plan to extend our analysis and
questionnaire to the Big Five and lower-label facets of each one, in
order to obtain a more comprehensive view on the role of personality
traits in financial decisions.

The time preference result is also consistent with related literature in
the sense that there is evidence that people who have microcredits tend
to be present-biased (Meier and Sprenger, 2010; Bauer *et al.*, 2012).
However, a temporal inconsistency known as hyperbolic discounting
(Laibson, 1997) is observed here: the individuals who belong to the
*Current* group are present-biased in the short-term while more patient
in the medium term. Beside this, we believe that, contradictory as it
might seem, a more diligent and present-biased individual in the
short-term has higher probability of a timely credit repayment. This
finding supports the idea that personality traits and time preferences
play a complementary role in explaining individuals' life outcomes
(Almlund *et al*., 2011; Becker *et al*., 2012; Rustichini *et al*.,
2012). While the possible relationship between preferences and
personality traits is beyond the scope of this paper, it should be
explored in future research.

The second main finding of this paper is that cognitive ability, while
statistically significant, does not explain the probability of belonging
to the Current group. Contrary to what we had expected, the lower an
individual's cognitive ability, the likelier they are to be in the
Current group. This result is also at odds with prevailing ideas in the
literature on the subject (Christelis *et al.,* 2010; McArdle *et al.,*
2011; Grinblatt *et al.*, 2011; Agarwal and Mazumder, 2013; Cole *et
al.,* 2014). Notwithstanding, Baklouti (2013) found that borrowers with
the lowest educational levels exhibit the highest repayment rate, the
idea being that clients with a low level of education tend to have fewer
financial alternatives, and therefore value the loans they do obtain
more highly. This finding brings support to the conclusion of Muhammad
Yunus that poor borrowers, who are completely financially excluded, are
more trustworthy than rich ones. This might be an explanation for the
negative relationship that is found between cognitive characteristics
and repayment behavior, particularly in a country with high levels of
financial exclusion of the low-income population (Demirgüç-Kunt et al.,
2015).

It should be noted, however, that this result could also be due in part
to measurement errors. Specifically, in this sample nobody provided a
correct answer to the question included to measure cognitive ability,
and the answers to questions included to measure numerical ability
(simple interest calculation) and financial literacy (knowledge of the
concept of inflation) were not answered correctly by most of the sampled
individuals. Although these questions have proved to be appropriate to
build valid indicators of cognitive characteristics and financial
literacy for individuals in developed economies (Frederick, 2005; Burks
*et al.*, 2009; Lusardi and Mitchell, 2014), it is possible that
non-verbal IQ tests, such as Raven's Matrices and Digit test, could be
more effective at measuring individuals' cognitive ability for
developing economies and low-income populations (Arráiz et al., 2015).

Given the nature of survey data, a possible selection bias could be
present. In the sample, around 14% of the people completed the survey;
this may be due to the lack of monetary incentives. However, given that
the sample was taken from the clients of Provident that were active at
the moment of the survey, there is information about who completed the
survey and who did not. We found no statistical difference between these
two groups in the variables of the age, number of active loans or
gender. The complete analysis can be found in the online appendix.

That said, given the lack of access to data from other companies, it is
impossible to evaluate if Provident's clients are similar to the general
population of creditors at any level. For this reason, the results
should be taken with caution if intended to apply to other populations.
However, given the consistency with the literature, the possible bias
could have affected the estimates, but not to the extent of
contradicting the direction or significance of the effects.

Finally, contrary to refinancing repayment studies within the
traditional microfinance literature (Armendariz De Aghion and Murdoch,
2000), in this sample, the refinancing incentive does not constitute a
powerful tool for getting this institution's clients to repay on time.
Our result however is consistent with the finding that individuals that
are in the *Current* group are characterized by short-term impatience.
We conclude by highlighting that the preceding results and discussion
provide a reason for future research that integrates new personality and
cognition theories with traditional microfinance repayment theory.

# References {-}
\small
1.  Agarwal, S., Mazumder, B. 2013. Cognitive Abilities and Household
    Financial Decision Making. *American Economic Journal: Applied
    Economics* 5:193-207.

2.  Aldasoro, B. 2017. Informe Final: Estudio sobre las Tasas de Interés
    de Microcrédito en México, 2017. Fundación Alemana Servicios.
    Available at:
    [[www.gob.mx]{.underline}](https://www.gob.mx/cms/uploads/attachment/file/275439/Estudio_sobre_las_Tasas_de_Interes_de_Microcredito_en_Mexico.pdf)

3.  Almlund, M., Duckworth, A.L., Heckman, J.J., Kautz, T. 2011.
    Personality Psychology and Economics. In: Hanushek, E., Machin, S.,
    Woessmann, L. (eds), Handbook of the Economics of Education 4:
    1-181.

4.  Ameriks, J., Caplin, A., Lehan, J. 2003. Wealth Accumulation and the
    Propensity to Plan. *Quarterly Journal of Economics* 118: 1007-1048.

5.  Angelucci, M., Karlan, D., Zinman, J. 2015. Microcredit Impacts:
    Evidence from a Randomized Microcredit Placement Experiment by
    Compartamos Banco. *American Economic Journal: Applied Economics* 7:
    151-182.

6.  Armendáriz De Aghion, B., Morduch, J. 2000. Microfinance Beyond
    Group Lending. *Economics of Transition* 8: 401-420.

7.  Armendáriz, B., Morduch, J. 2010. *The Economics of
    Microfinance* (2nd ed.). The MIT Press: Cambridge, MA.

8.  Arráiz, I., Bruhn, M. and Stucchi, R. 2015. Psychometrics as a tool
    to improve screening and access to credit. World Bank Policy
    Research Working Paper No. 7506. Available
    at: [[https://ssrn.com]{.underline}](https://ssrn.com/abstract=2698969)

9.  Attanasio, O., Augsburg, B., De Haas, R., Fitzsimons, E.,
    Harmgard, H. The Impacts of Microfinance: Evidence from
    Joint-Liability Lending in Mongolia. *American Economic Journal:
    Applied Economics* 7: 90-122.

10. Augsburg, B., De Haas, R., Harmgard, H., Meghir, C. 2015. The
    Impacts of Microcredit: Evidence from Bosnia and Herzegovina.
    *American Economic Journal: Applied Economics* 7: 183-203.

11. Baklouti, I. 2013. Determinants of Microcredit Repayment: The Case
    of Tunisian Microfinance Bank. *African Development Review* 25:
    370-82.

12. Banerjee, A., Duflo, E., Glennester, R., Kinnan, C. 2015. The
    Miracle of Microfinance? Evidence from a Randomized Evaluation.
    *American Economic Journal: Applied Economics* 7: 22-53.

13. Basu, K. 2016. A Behavioral Model of Simultaneous Borrowing and
    Saving. *Oxford Economic Papers* 68: 1166-74.

14. Bauer, M. Chytilová, J., Murdoch, J. 2012. Behavioral Foundations of
    Microcredit: Experimental and Survey Evidence from Rural India.
    *American Economic Review* 201: 1118-39.

15. Becker, A., Deckers, T., Dohmen, T., Falk, A., Kosse, F. 2012. The
    relationship between economic preferences and psychological
    personality measures. *Annual Review of Economics* 4: 453-78.

16. Bhatt, N., Tang, S. 2002. Determinants of Repayment in Microcredit:
    Evidence from Programs in the United States. International *Journal
    of Urban and Regional Research* 26: 360-376.

17. Borghans, L., Golsteyn, B., Heckman, J., Humphries, J. 2011.
    Identification Problems in Personality Psychology. *Personality and
    Individual Differences* 43: 972-1059.

18. Burks, S. V., Carpenter, J. P. Goette, L., Rustichini A. 2009.
    Cognitive skills affect economic preferences, strategic behavior,
    and job attachment. *Proceedings of the National Academy of
    Sciences* 106: 7745-50.

19. Christelis, D., Jappelli, T., Padula, M. 2010 Cognitive abilities
    and portfolio choice. *European Economic Review* 54: 18-38.

20. Cole, S., Paulson, A., Shastry, G. 2014. Smart Money? The Effect of
    Education on Financial Outcomes. *Review of Financial Studies* 27:
    2022-51.

21. Cotler, P. 2013. Las tasas activas de interés en el sector
    microfinanciero de México: Un estudio de caso. Econoquantum Revista
    de Economía y Negocios 10: 7-26.

22. Crépon, B., Devoto, F., Duflo, E., Parienté, W. 2015. Estimating the
    Impact of Microfinance on those who Take It Up: Evidence from a
    Randomized Experiment in Morocco. *American Economic Journal:
    Applied Economics* 7: 123-150.

23. Demirgüç-Kunt, A., Klapper L., Singer D., Van Oudheusden P. 2015.
    The Global Findex Database, Measuring Financial Inclusion around the
    World. World Bank Policy Research Working Paper Series N° WPS7255.

24. D'Espallier, B., Guérin, I., Mersland, R. 2011. Women and repayment
    in microfinance: A global analysis. *World Development* 39: 758-72.

25. Duckworth, A., Quinn, P. 2009. Development and validation of the
    Short Grit Scale (Grit-S). *Journal of Personality Assessment* 91:
    166-74.

26. Eskreis-Winkler, L., Shulman, E., Beal, S., Duckworth, A.L. 2014.
    The Grit Effect: Predicting Retention in the Military, the
    Workplace, School and Marriage. Frontiers in Psychology:
    [[http://dx.doi.org/10.3389/fpsyg.2014.00036]{.underline}](http://dx.doi.org/10.3389/fpsyg.2014.00036)

27. Frederick, S. 2005. Cognitive reflection and decision making. *The
    Journal of Economic Perspectives* 19: 25-42.

28. Gerardi, K., Goette L., Meier, S. 2013. Numerical ability predicts
    mortgage default. *Proceedings of the National Academy of Sciences*
    110: 11267--71.

29. Griffin, D., Husted. B. Social Sanctions or Social Relations?
    Microfinance in Mexico. *Journal of Business Research* 68:
    2579-2587.

30. Grinblatt, M., Keloharju, M., Linnainmaa, L. 2011. IQ and Stock
    Market Participation. *Journal of Finance* 66: 2121-64.

31. Heckman, J. 1981. Heterogeneity and State Dependence. NBER Chapters
    in: Studies in Labor Markets: 91-140.

32. Heckman, J., Stixrud, J., Urzua, S. 2006. The Effects of Cognitive
    and Noncognitive Abilities on Labor Market Outcomes and Social
    Behavior. *Journal of Labor Economics* 24: 411-82.

33. Heckman, J., Kautz, T. 2012. Hard Evidence on Soft Skills. *Labour
    Economics* 19: 451-64.

34. Heidhues, P., Koszegi, B. 2010. Exploiting Naivete about
    Self-Control in the Credit Market. *American Economic Review* 100:
    2279-2303.

35. Hermes, N., Lensink, R. 2011. Microfinance: Its Impact, Outreach,
    and Sustainability. *World Development* 39: 875-81.

36. Jamshidinavid, B., Chavoshani, C., Amiri, S. 2012. The Impact of
    Demographic and Psychological Characteristics on the Investment
    Prejudices in Tehran Stock. *European Journal of Business and Social
    Sciences* 1: 41-53.

37. Kaufmann, C. 2012. "The Influence of Information Presentation,
    Psychological Mechanisms, and Personal Characteristics of
    Households' Financial Decision Making." Doctoral Thesis, Universitat
    Mannheim.

38. Kausel, E., Culbertson, S., Madrid, H. 2016. "Overconfidence in
    Personnel Selection: When and Why Unstructured Interview Information
    Can Hurt Hiring Decisions." *Organizational Behavior and Human
    Decision Processes,* 137: 27-44.

39. Klinger, B., Castro, L., Szenkman, P., Khwaja, A. 2013a. Unlocking
    SME Finance in Argentina with Psychometrics. *IDB Technical Note. *

40. Klinger, B., Khwaja, A., Del Carpio, C. 2013b. Enterprising
    Psychometrics and Poverty Reduction. *Springer Science and Business
    Media.*

41. Laibson, D. 1997. Golden Eggs and Hyperbolic Discounting. *Quarterly
    Journal of Economics* 112: 443-77.

42. Lusardi, A., Mitchell, O. 2014. The economic importance of financial
    literacy: theory and evidence. *Journal of Economic Literature* 52:
    5-44.

43. McArdle, J., Smith, J., Willis, R. 2011. "Cognition and Economic
    Outcomes in the Health and Retirement Survey". In Wise, D. (ed.),
    *Explorations of the Economics of Aging.* The University of Chicago
    Press, Chicago.

44. McCarthy, Y. 2011. Behavioral Characteristics and Financial
    Distress. ECB Working Paper 1303, European Central Bank, Frankfurt,
    Germany.

45. Meier, S., Sprenger, C. 2010. Present-Biased Preferences and Credit
    Card Borrowing. *American Economic Journal: Applied Economics* 2:
    193-210.

46. Nawai, N., Shariff, M. 2012. Factors affecting repayment performance
    in microfinance programs in Malaysia. *Procedia -- Social and
    Behavioral Sciences* 62: 806-11.

47. OECD INFE. 2011. Measuring Financial Literacy: Core Questionnaire in
    Measuring Financial Literacy: Questionnaire and Guidance Notes for
    conducting an Internationally Comparable Survey of Financial
    literacy. Paris: OECD.

48. Prevoo, T., ter Weel, B. 2015. The importance of conscientiousness
    for socio-economic outcomes: evidence from the British Cohort
    Study*. Oxford Economic Papers* 67: 918-48.

49. Roa, M. J., Garrón, I., Barboza, J. 2019. Financial Decisions and
    Financial Capabilities in the Andean Region. *Journal of Consumer
    Affairs*, *53*(2), 296-323.

50. Roy, A. 1951. Some Thoughts on the Distribution of Earnings. *Oxford
    Economic Papers*, 3: 135-46.

51. Rustichini, A., De Young, C., Anderson, J., Burks, S. 2016. "Toward
    the integration of personality theory and decision theory in
    explaining economic behaviour: An experimental investigation."
    *Journal of Behavioral and Experimental Economics*, 64: 122-137.

52. Van den Berg, M., Lensink, R., Servin, R. 2015. Loan Officer's
    Gender and Microfinance Repayment Rates. *Journal of Development
    Studies*, 51: 1241-12.

53. Van Rooij, M., Lusardi, A., Alessie, R. 2011. Financial literacy and
    stock market participation. *Journal of Financial Economics* 101:
    449-47.
    

\newpage
<!-- \mbox{} to add an empy numbered page-->

[^1]: A detailed description of this questionnaire can be found in the
    On-line Appendix 1.

[^2]: The average exchange rate in the period from January to April 2014
    was 13.19 Mexican pesos per US Dollar.

[^3]: the sample is from 2014. We had access to the data a significant
    while after the sampling was made, and then we had to provide a
    statistical analysis to Provident, which also took some time. The
    agreement with Provident was that after the report, we could use the
    data to write a research paper. At that point, a more detailed
    analysis was required to take full advantage of the dataset and we
    modified the model specification accordingly; unfortunately, we
    encountered several technical difficulties in the statistical
    methodology. Such corrections took us more time than we care to
    admit. Once we considered that the estimation was appropriate, we
    asked for the informal opinion of several experts in the field,
    which was also a lengthier process than initially expected.

[^4]: The weights, provided by Provident, are: *Current* 28.2%, *Low
    arrear* 56.0%, and *High arrear* 15.8%.

[^5]: An Ordered Logit model (o-logit) is a regression model
    particularly well suited for ordinal dependent variables, such as
    the one in this study (Current/Low/High arrear), where the distance
    between adjacent categories is unknown. The variable has been
    categorized incrementally (Current\<Low\<High arrear). We compared
    Ordered Logit (o-logit) results with those of an Ordered Probit
    (o-probit), a model also well suited for this type of dependent
    variable (the latter assumes a cumulative distribution function of
    the standard normal distribution instead of that of a logistic
    distribution in a o-logit model). The statistical results of the
    o-logit model were far better than those of the o-probit (results
    available upon request). The multinomial logit and the multinomial
    probit models were discarded because the outcomes of the dataset
    must be ordered (ranked), and these models seem better suited for
    categorical data which cannot be ordered in any meaningful way.
    Being the o-logit a particular case of the multinomial logistic
    regression, the later model could have been an option. Nonetheless,
    the results of the former model are satisfactory, and the more
    sophisticate option was not considered necessary. Similarly, the
    cumulative logit regression was not considered as it is more limited
    than the o-logit.

[^6]: PCA analysis yields a linear combination of the variables that
    maximizes the variance, i.e., it maximizes the information subject
    to a parametric constraint: the sum of the squared weights must be
    equal to 1.

[^7]: The weights were: -0.1413 (question 9), -0.0842 (question 12),
    -0.6754 (question 13), and 0.7188 (scholarship). The complete
    analysis is included in the appendix.

[^8]: The data and the code to estimate our econometric results can be
    found in the On-line Appendix 3.
